---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/UBESP-DCTV/garminer.svg?branch=master)](https://travis-ci.org/UBESP-DCTV/garminer)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/UBESP-DCTV/garminer?branch=master&svg=true)](https://ci.appveyor.com/project/UBESP-DCTV/garminer)
[![Coverage status](https://codecov.io/gh/UBESP-DCTV/garminer/branch/master/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/garminer?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/garminer)](https://cran.r-project.org/package=garminer)

# garminer

The goal of garminer is to provide a set of utility function to extract
information and get insights from Garmin FIT files.

## Installation

You can install the develop version of garminer from
[GITHUB](https://github.com) with:

```{r installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/garminer")
```


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
to <https://github.com/UBESP-DCTV/garminer/issues>


## Code of conduct
Please note that this project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this
project you agree to abide by its terms.
